Type cones of $\b{g}$-vector fans

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
clean 3.4
todo notes

\vincent{Link to \cref{sec:clusterCategories}.}
\vincent{Pictures quivers.}

@@

%This statement will be proved in full generality in \cref{???}.
%We proved it in \cref{prop:extremalExchangeablePairsAsso} for acyclic initial seeds in type~$A$. To provide an intuition of the result, we sketch here a proof for arbitrary initial seeds in type~$A$.
%
%\begin{proof}[Sketch of \cref{thm:extremalExchangeablePairsCA} in type~$A$]
%We need to prove that the normal vector~$\b{n}(\B_\circ, y, y')$ for any exchangeable pair~$\{y,y'\}$ is a positive linear combination of the vectors~$\b{n}(\B_\circ, x, x')$ for non-initial meshes.
%\vincent{Do we really want to do that?}
%\end{proof}

@@

In this section, we need to restrict even further the family of gentle quivers we consider.

\begin{definition}
We say that a gentle quiver~$\quiver$ is \defn{simple} when
\begin{itemize}
\item it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
\item it contains no cycle of length~$2$.
\end{itemize}
\end{definition}

Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
In particular, the classical associahedron is the gentle associahedron of a simple gentle quiver.
We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.

@@

\begin{proposition}
For any simple gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
\end{proposition}

@@

\begin{proposition}
\label{prop:extremalExchangeablePairsNKC}
For any simple gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
\end{proposition}

@@

\begin{corollary}
\label{coro:simplicialTypeConeNKC}
For any simple gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
\end{corollary}

@@

\begin{corollary}
\label{coro:allPolytopalRealizationsNKC}
For any simple gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{corollary}

@@

@@

\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}

\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}\label{sect::applications-g-vectors}

@@

@@

@@

>>>>

\vincent{Link to \cref{sec:clusterCategories}.}
\vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
\vincent{Pictures quivers.}

@@

\vincent{Should we give a type $A$ intuition here?}
%This statement will be proved in full generality in \cref{???}.
%We proved it in \cref{prop:extremalExchangeablePairsAsso} for acyclic initial seeds in type~$A$. To provide an intuition of the result, we sketch here a proof for arbitrary initial seeds in type~$A$.
%
%\begin{proof}[Sketch of \cref{thm:extremalExchangeablePairsCA} in type~$A$]
%We need to prove that the normal vector~$\b{n}(\B_\circ, y, y')$ for any exchangeable pair~$\{y,y'\}$ is a positive linear combination of the vectors~$\b{n}(\B_\circ, x, x')$ for non-initial meshes.
%\vincent{Do we really want to do that?}
%\end{proof}

@@

In this section, we need to restrict even further the family of gentle quivers we consider.
\vincent{rephrase}

\begin{definition}
A gentle quiver~$\quiver$ is called:
\begin{itemize}
\item \defn{brick}: it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
\item \defn{$2$-acyclic}: it contains no cycle of length~$2$.
\end{itemize}
\end{definition}

Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
In particular, the classical associahedron is the gentle associahedron of a brick $2$-acyclic gentle quiver.
We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.

@@

\begin{proposition}
For any brick $2$-acyclic gentle quiver~$\quiver$ and any string~$\sigma \in \strings$, the walks~$\cc{\sigma}$ and~$\hh{\sigma}$ are exchangeable with distinguished substring~$\sigma$.
\end{proposition}

@@

\begin{proposition}
\label{prop:extremalExchangeablePairsNKC}
For any brick $2$-acyclic gentle quiver~$\quiver$, the extremal exchangeable pairs for the non-kissing fan of~$\quiver$ are precisely the pairs~$\{\cc{\sigma}, \hh{\sigma}\}$ for all strings~$\sigma \in \strings$.
\end{proposition}

@@

\begin{corollary}
\label{coro:simplicialTypeConeNKC}
For any brick $2$-acyclic gentle quiver~$\quiver$, the type cone~$\typeCone(\gvectorFan[\quiver])$ of the non-kissing fan~$\quiver$ is simplicial.
\end{corollary}

@@

\begin{corollary}
\label{coro:allPolytopalRealizationsNKC}
For any brick $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{corollary}

@@

\vincent{All this section is wrong when the quiver is not brick or has a cycle of length~$2$.}

@@

\subsection{Application to~$\b g$-vectors of cluster algebras of finite type}
\label{sect::applications-g-vectors}

@@

\vincent{Here should come the proof of \cref{prop:meshMutations}.}

\vincent{Here should come the proof of \cref{prop:uniqueExchangePropertyCA}.}

@@

\vincent{Here should come the proof of \cref{prop:exchangeablePairsNKC}.}

@@

\vincent{Here should be explained that the gentle algebra result is a special case of this.}
